Gravitational-wave sensitivity curves

### 2014-07-03 Introduction.tex
Section 2

Since the GW signal and detector output are both real it follows that $\tilde{h}(-f)=\tilde{h}^{*}(f)$ and $\tilde{n}(-f)=\tilde{n}^{*}(f)$; therefore, $S_{n}(f)=S_{n}(-f)$. The fact that $S_{n}(f)$ is an even function means that Fourier integrals over all frequencies can instead be written as integrals over positive frequencies only, e.g., (\ref{eq:meansquare1}) and (\ref{eq:snrinnerprod})); it is for this reason that $S_{n}(f)$ is called the \emph{one-sided} power spectral density.\footnote{An alternative convention is to use the two-sided power spectral density $S^{(2)}_{n}(f) = S_{n}(f)/2$.}

@@

Cosmological studies often work in terms of the dimensionless quantity $\Omega_{\mathrm{GW}}$, the energy density per logarithmic frequency interval normalised to the critical density of the universe:
\begin{equation}\label{eq:omega}
\Omega_{\mathrm{GW}}(f)= \frac{fS_{\mathrm{E}}(f)}{\rho_{\mathrm{c}}c^{2}} = \frac{\pi}{4G\rho_{c}}f^{3}S_{h}(f) = \frac{\pi}{4G\rho_{c}}f^{2}h_{c}(f)^{2}\; .
\end{equation}
The critical density of the universe is
\begin{equation}
\rho_{\mathrm{c}}=3H_{0}^{2}/8\pi G \;,
\label{eq:crit-density}
\end{equation}
 where $H_{0}$ is the Hubble constant which is commonly parametrized as
\begin{equation}
H_0 =h_{100}\times 100~\mathrm{km\,s^{-1}\,Mpc^{-1}}.
\end{equation}
The reduced Hubble parameter $h_{100}$ has nothing to do with strain. The most common quantity related to energy density to be plotted on sensitivity curves is $\Omega_{\mathrm{GW}}h_{100}^{2}$ (figure \ref{fig:omega}) as this removes sensitivity to the measured value of the Hubble constant.

>>>>

Since the GW signal and detector output are both real it follows that $\tilde{h}(-f)=\tilde{h}^{*}(f)$ and $\tilde{n}(-f)=\tilde{n}^{*}(f)$; therefore, $S_{n}(f)=S_{n}(-f)$. The fact that $S_{n}(f)$ is an even function means that Fourier integrals over all frequencies can instead be written as integrals over positive frequencies only, e.g., (\ref{eq:meansquare1}) and (\ref{eq:snrinnerprod}); it is for this reason that $S_{n}(f)$ is called the \emph{one-sided} power spectral density.\footnote{An alternative convention is to use the two-sided power spectral density $S^{(2)}_{n}(f) = S_{n}(f)/2$.}

@@

Cosmological studies often work in terms of the dimensionless quantity $\Omega_{\mathrm{GW}}$, the energy density per logarithmic frequency interval normalised to the critical density of the universe:
\begin{equation}
\label{eq:omega}
\Omega_{\mathrm{GW}}(f)= \frac{fS_{\mathrm{E}}(f)}{\rho_{\mathrm{c}}c^{2}} = \frac{\pi}{4G\rho_{c}}f^{3}S_{h}(f) = \frac{\pi}{4G\rho_{c}}f^{2}h_{c}(f)^{2}\; .
\end{equation}
The critical density of the universe is
\begin{equation}
\rho_{\mathrm{c}}=3H_{0}^{2}/8\pi G \;,
\label{eq:crit-density}
\end{equation}
 where $H_{0}$ is the Hubble constant which is commonly parametrized as
\begin{equation}
H_0 =h_{100}\times 100~\mathrm{km\,s^{-1}\,Mpc^{-1}}.
\end{equation}
The reduced Hubble parameter $h_{100}$ has nothing to do with strain. The most common quantity related to energy density to be plotted on sensitivity curves is $\Omega_{\mathrm{GW}}h_{100}^{2}$ (figure \ref{fig:omega}) as this removes sensitivity to the measured value of the Hubble constant.
